---
title: "Assigment - kNN DIY"
author:
  - name author here - Robert Houlden
  - name reviewer here - Boyer Samuel
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
   html_notebook:
    toc: true
    toc_depth: 2
---

##Insert packages
```{r}
library(tidyverse)
library(googlesheets4)
library(class)
library(caret)
```
##Insert data frame
```{r}
url <- "https://raw.githubusercontent.com/HAN-M3DM-Data-Mining/data-mining-s2y2122-R-Houlden/master/datasets/KNN-hcvdat0.csv"
rawDF <- read_csv(url)
```

###Business Understanding###
##We can use measures of AST & GGT to determine if a patient has hepatits.

#AST = 10-40 (Higher = Liver Issue)
#GGT = 5-40 (Higher = Liver Issue)

##Data Understanding
##Get some basic information about the data set
```{r}
str(rawDF)
```
##615 rows of data and 14 variables


##Preparation

#Columns ID, Age, Sex, CHE, CHOL, CREA, ALP, ALB, ATL, BIL, and PROT are not required so they can be removed
```{r}
cleanDF <- rawDF[-1]
head(cleanDF)
cleanDF <- select(cleanDF, -Age, -Sex, -CHOL, -ALP, -ALT, -PROT, -ALB, -BIL, -CREA, -CHE)
```

##I don't need Suspect Bloor Donor, Fibrosis, or Cirrhosis. So they are removed
```{r}
cleanDF[-c(534:540, 565:615),]
cleanDF <- cleanDF[-c(534:540, 565:615),]
```

#I want to predict the Category, either Blood Donor or Hepatitis

```{r}
cntCateg <- table(cleanDF$Category)
propCateg <- round(prop.table(cntCateg) * 100 , digits = 1)

cntCateg
propCateg
```

##Rename variables so that they are factors
```{r}
cleanDF$Category <- factor(cleanDF$Category, levels = c("0=Blood Donor", "1=Hepatitis"), labels = c("", "")) %>% relevel("Blood Donor")
head(cleanDF, 10)
```

##Have a closer look at our data
```{r}
summary(cleanDF[c("AST","GGT")])
```

##Make normalize function and test it
#Test
```{r}
normalize <-  {return ((x - min(x)) / (max(x) - min(x)))}

testSet1 <- c(1:5)
testSet2 <- c(1:5) * 10

cat("testSet1:", testSet1, "\n")
cat("testSet2:", testSet2, "\n")
```
#Implementation of normalize function
```{r}
nCols <- dim(cleanDF)[2]
cleanDF_n <- sapply(2:nCols,
                    function(x) {
  normalize(cleanDF[,x])
}) %>% as.data.frame()

summary(cleanDF_n[c("AST","GGT")])
```
##Split data into training and test sets
```{r}
trainDF_feat <- cleanDF_n[1:480,  ]
testDF_feat <- cleanDF_n[481:557,  ]
```
##Make training labels
```{r}
trainDF_labels <- cleanDF[1:480,  1]

```

##Modelling & Evalutaion
```{r}
cleanDF_test_pred <- knn(train = as.matrix(trainDF_feat), test = as.matrix(testDF_feat), cl = as.matrix(trainDF_labels), k = 7)
head(cleanDF_test_pred)
```
##Run confusion matrix for results of KNN
```{r}
confusionMatrix(cleanDF_test_pred, testDF_labels[[1]], positive = NULL, dnn = c("Prediction", "True"))
```

